Quantifying the importance of an inference model in Bayesian phylogenetics

### 2020-03-23 supplement.tex
More pics in supmat

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_23/example_23/314/errors.png}
  \caption{Lowest likelihood}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_23/example_23/315/errors.png}
  \caption{Between lowest and median likelihood}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_23/example_23/316/errors.png}
  \caption{Median likelihood}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_23/example_23/317/errors.png}
  \caption{Between median and highest likelihood}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_23/example_23/318/errors.png}
  \caption{Highest likelihood}
\end{figure}

>>>>

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_23/errors_low.png}
  \caption{Lowest likelihood}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_23/errors_mid.png}
  \caption{Median likelihood}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_23/errors_high.png}
  \caption{Highest likelihood}
\end{figure}
